Manuscript Draft\\ \vspace{2cm} What is long-distance dispersal? And a taxonomy of dispersal events

### 2016-06-17 Manuscript/MS- What is LDD.tex
Minor edits to Table and Figure legends.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS Draft Journal of Ecology Special Issue, Dispersal - 
%% Pedro - 07 April 2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Headers

\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\pagestyle{plain}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage{lscape}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{longtable}
\usepackage{rotating}                                                                                    
\newcommand{\tab}{\hspace{5mm}}
\usepackage{tabularx} 
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
\usepackage[left]{lineno}
\usepackage{caption}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy}     % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{{\tiny Jordano - What is long-distance dispersal?}}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}
\usepackage{parskip}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title page
\begin{document}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TABLES
%-------------------------------------------------------------------- Table 1
\pagestyle{empty}
\begin{landscape}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\oddsidemargin  0.0in
%	\evensidemargin 0.0in
%	\textwidth      8.5in
	\headheight     3cm
%	\topmargin      0.0in
%	\textheight=8.0in
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\captionsetup{width=20cm}%.75\textwidth}
\caption{Types of dispersal as a function of population area limits and genetic neighborhood limits.}
\vspace{0.5cm}
  \begin{tabular}{lll}
    \hline
\\&Population geographic limit    &  \\\\
Genetic neighborhood limit     &Within &Outside \\\\
    \hline
\\Within    &  Local, short-distance \linebreak dispersal, $SDD_{loc}$  
          &  Within neighborhood, \linebreak long-distance dispersal, $LDD_{neigh}$ \\\\
Outside   &     Local, long-distance \linebreak dispersal, $LDD_{loc}$    
          &  Strict sense \linebreak long-distance dispersal, $LDD_{ss}$\\\\ 
    \hline
  \end{tabular}
\end{table}
\end{landscape}

@@

\section*{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% References
%%% Unnumbered Literature Cited
\bibliographystyle{bes}        %Compile with bes.bst style file
\bibliography{MS_BES}

@@

\textbf{Figure 2}. Schematic representation of different types of long-distance dispersal events in relation to the geographical limits of local populations (dashed lines) and the genetic neighborhood size (grey area) of specific individual plants. Dispersal events (arrows) can be classified depending on their actual incidence on propagule movement outside these reference areas (Table 1).\\

@@

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the seed dispersal of \textit{Prunus mahaleb}.\\ 
\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS Draft Journal of Ecology Special Issue, Dispersal - 
%% Pedro - 07 April 2016
%----------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Headers
\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\pagestyle{plain}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage{lscape}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{longtable}
\usepackage{rotating}                                                                                    
\newcommand{\tab}{\hspace{5mm}}
\usepackage{tabularx} 
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
\usepackage[left]{lineno}
\usepackage{caption}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy}     % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{{\tiny Jordano - What is long-distance dispersal?}}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}
\usepackage{parskip}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title page
\begin{document}

@@

%\section*{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% References
%%% Unnumbered Literature Cited
\bibliographystyle{bes}        %Compile with bes.bst style file
\bibliography{MS_BES}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TABLES
%-------------------------------------------------------------------- Table 1
\pagestyle{empty}
\begin{landscape}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\oddsidemargin  0.0in
%	\evensidemargin 0.0in
%	\textwidth      8.5in
	\headheight     3cm
%	\topmargin      0.0in
%	\textheight=8.0in
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\captionsetup{width=20cm}%.75\textwidth}
\caption{Types of dispersal as a function of population area limits and genetic neighborhood limits. See Fig. 2 for a graphical representation of the four scenarios.}
\vspace{0.5cm}
  \begin{tabular}{lll}
    \hline
\\&Population geographic limit    &  \\\\
Genetic neighborhood limit     &Within &Outside \\\\
    \hline
\\Within    &  Local, short-distance \linebreak dispersal, $SDD_{loc}$  
          &  Within neighborhood, \linebreak long-distance dispersal, $LDD_{neigh}$ \\\\
Outside   &     Local, long-distance \linebreak dispersal, $LDD_{loc}$    
          &  Strict sense \linebreak long-distance dispersal, $LDD_{ss}$\\\\ 
    \hline
  \end{tabular}
\end{table}
\end{landscape}

@@

@@

\textbf{Figure 2}. Schematic representation of different types of long-distance dispersal events in relation to the geographical limits of local populations (dashed lines) and the genetic neighborhood size (grey area) of specific individual plants. Dispersal events (arrows) can be classified depending on their actual incidence on propagule movement outside these spatially-explicit reference areas (Table 1).\\

@@

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the short- and long-distance seed dispersal events for \textit{Prunus mahaleb} according to the classification in Table 1.\\ 
\newpage
